Quantum parallel parallel Markov chain Monte Carlo

### 2021-11-23 main.tex
expo search algorithm figure
expop search figure in manu
caption on figure 2

>>>>

 \begin{figure}[!t]
 	\centering
 	\includegraphics[width=0.9\linewidth]{expoSearch.pdf}
 	\caption{Total number of oracle evaluations required by quantum exponential searching algorithm \citep{boyer1998tight} for different numbers of solutions $M$ and search set sizes $N$ from 500 independent simulations each.  Horizontal lines at $\frac{9}{4}\sqrt{N}$ represent upper bounds on expected total number of evaluations to obtain a solution for the $M=1$ problem.}\label{fig:expo}
 \end{figure}

 \todo{caption}
